Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-30 manuscript.Rmd
Add revisions

This linguistic cohesion metric is similar to *term frequency-inverse document
frequency* [tf-idf; see also @jones1972statistical;
@robertson2004understanding]. However, the method focuses more squarely on terms
(i.e., agnostic to the number of documents in the corpus), aggregates at a
higher semantic level (i.e., summing across words), and accounts for linguistic
novelty relative to the pair and the corpus (i.e., ratio of Eq. 1 to Eq. 2). The
social cohesion calculation was performed on the tweet corpus containing English
tweets. All hashtags and URLs were included in the analysis. The raw social
cohesion time series can be seen in Figure \@ref(fig:raw-cohesion-ts).

@@

To perform categorical CRQA, the time series must be converted to the same
scale, while still preserving a sampling rate that respects the native timescale
of the system [cf. Nyquist frequency in signal processing;
@grenander1959probability]. In other words, a system that changes every day must
be sampled more often than a system that changes every year and less often than
a system that changes every hour. However, to compare two time series with CRQA,
the two time series must be sampled at the same frequency as one another.

Because the social cohesion and event data have different scales and values, we
converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles (e.g.,
Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of different
levels of social cohesion and counts of all, positive, and negative events on
each day. We implemented CRQA using the `crqa` package [@R-crqa] for R
[@R-base].

@@

The percentage of recurrent points to total possible points is a metric called
the *recurrence rate* (*RR*). This metric gives a general description of how
frequently the time series are sharing the same states. In the current study, a
recurrent point would indicate that the level of social cohesion and frequency
of events were at the same intensity.

@@

Using the real deciled time series of social cohesion, count of all events,
count of positive events, and count of negative events, we conducted a series of
permutation tests (one for the comparison between social cohesion and each type
of event count) to determine statistical difference from chance for each CRQA
metric. Using the `sample` function in base R [@R-base], $1000$ permuted time
series were created for each of the real time series. CRQA was then run $1000$
times for social cohesion and count of all events, social cohesion and count of
positive events, and social cohesion and count of negative events using the
permuted time series. This resulted in $1000$ results for each of the CRQA
metrics for each combination of time series. Statistical significance from
chance was set at the 95th and 99th percentiles of the metrics from the permuted
CRQ analyses. Given that a permutation test is similar to bootstrapping but does
not include replacement, all real recurrent points were included in each CRQA
analysis, leaving RR constant across all permutations. Thus, RR is not included
in the inferential tests.

@@

A permutation test for the CRQA of social cohesion and count of all events found
a statistical difference from chance for DET, NRLINE, and LAM. All other metrics
did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).

A permutation test for the CRQA of social cohesion and count of positive events
found a statistical difference from chance for DET, NRLINE, maxL, LAM, and TT.
All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
\autoref{table-1}).

@@

### Syria as Source and Target
A permutation test for the CRQA of social cohesion and count of all events found
a statistical difference from chance for DET, maxL, and LAM. All other metrics
were non-significant (Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of positive events
found a statistical difference from chance for DET, L, ENTR, rENTR, and LAM
(Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of negative events
found no statistical difference from chance for and metrics (Figure
\@ref(fig:plot-rp-source-targ); \autoref{table-2}).

>>>>

This linguistic cohesion metric is similar to *term frequency-inverse document
frequency* [tf-idf; see also @jones1972statistical;
@robertson2004understanding]. However, the method focuses more squarely on terms
(i.e., agnostic to the number of documents in the corpus), aggregates at a
higher semantic level (i.e., summing across words), and accounts for linguistic
novelty relative to the pair and the corpus (i.e., ratio of Eq. 1 to Eq. 2). The
social cohesion calculation was performed on the tweet corpus containing English
tweets. All hashtags were included in the analysis, while URLs were removed. The
raw social cohesion time series can be seen in Figure
\@ref(fig:raw-cohesion-ts).

@@

To perform categorical CRQA, the time series must be converted to the same
scale, while still preserving a sampling rate that respects the native timescale
of the system [cf. Nyquist frequency in signal processing;
@grenander1959probability]. In other words, a system that changes every day must
be sampled more often than a system that changes every year and less often than
a system that changes every hour. However, to compare two time series with CRQA,
the two time series must be sampled at the same frequency as one another.
Because the social cohesion and event data have different scales and values, we
converted each time series of daily values (e.g., Figure \@ref(fig:raw-ts)) into
deciles (e.g., Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of
different levels of social cohesion and counts of all, positive, and negative
events on each day. We implemented CRQA using the `crqa` package [@R-crqa] for R
[@R-base].

@@

The percentage of recurrent points to total possible points is a metric called
the *recurrence rate* (*RR*). This metric gives a general description of how
frequently the time series are sharing the same states. In the current study, a
recurrent point would indicate that the level of social cohesion and frequency
of events were at the same intensity for across two particular points in time
(in this case, one-day windows). Importantly, the nature of CRQA allows us to
quantify how a system shares similar states across time: In other words, it
identifies recurrence whether a window of shared intensity occurs on the same
day for the two time series or after a one-week gap between when the two time
series exhibit the same intensity.

@@

Using the real deciled time series of social cohesion, count of all events,
count of positive events, and count of negative events, we conducted a series of
permutation tests (one for the comparison between social cohesion and each type
of event count) to determine whether the observed measure is statistically different from chance for each CRQA
metric. Using the `sample` function in base R [@R-base], $1000$ permuted time
series were created for each of the real time series. CRQA was then run $1000$
times for social cohesion and count of all events, social cohesion and count of
positive events, and social cohesion and count of negative events using the
permuted time series. This resulted in $1000$ results for each of the CRQA
metrics for each combination of time series. Statistical significance from
chance was set at the 95th and 99th percentiles of the metrics from the permuted
CRQ analyses. Given that a permutation test is similar to bootstrapping but does
not include replacement, all real recurrent points were included in each CRQA
analysis, leaving RR constant across all permutations. Thus, RR is not included
in the inferential tests.

@@

A permutation test for the CRQA of social cohesion and count of all events found
a statistically significant difference from chance for DET, NRLINE, and LAM. All
other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
\autoref{table-1}).

A permutation test for the CRQA of social cohesion and count of positive events
found a statistically significant difference from chance for DET, NRLINE, maxL,
LAM, and TT. All other metrics did not reach significance (Figure
\@ref(fig:plot-rp-targ); \autoref{table-1}).

@@

### Syria as Source and Target
A permutation test for the CRQA of social cohesion and count of all events found
a statistically significant difference from chance for DET, maxL, and LAM. All
other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ);
\autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of positive events
found a statistically significant difference from chance for DET, L, ENTR,
rENTR, and LAM (Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of negative events
found no statistically significant difference from chance for and metrics
(Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
